Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-06 PaperBCJ.tex
Auto stash before merge of "master" and "origin/master"

One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 Parameters & LeNet & AlexNet & cNET & sNET \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 4500 & 3000 \\ 
  Accuracy(\%) & 78.84 & 95.266 & 99.33 & 90.4 \\
  Loss(\%) & 44.8471 & 12.7256 & 5.86 & 781.3 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:2}
\end{table}

Inside of the shown parameters in the Table {table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification. The following picture shows the process of training of the cNET \\
Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification. The following picture shows the process of training of the cNET. \\

@@

Although results given for the net are excellents, one of the main purposes of this paper is the implementation in real time, so the number of parameters to be computed must be a problem, so we considered to modify the net in order to improve the processing time. To achive this, it was neccesary to reduce the number of filters from 64 to 16, this permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy, the results of the processing will be explained with more detail in the next section.

@@

For this stage, we considered an extra dataset with 200 images of maize plants and 203 images of weed, the results were comparated between cNET with 64 and 16 filters, each one would be  
\begin{table}[h!]
\centering
\begin{tabular}{|l|c|c|p{2cm}|}  
 \hline
 \multicolumn{4}{ |c| }{GPU} \\
 \hline
   cNET & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{CPU} \\
 \hline
   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification \\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{CPU Raspberry Pi 3} \\
 \hline
   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification\\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 615 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 161 s \\ [0.75ex]
  \hline
\end{tabular}
\caption{Test}
\label{table:2}
\end{table}

>>>>

One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 Parameters & LeNet & AlexNet & cNET & sNET \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
  Accuracy(\%) & 86.48 & 93.86 & 95.33 & 80.4 \\
  Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:2}
\end{table}

Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission near to human classification. The following picture shows the process of training of the cNET. \\

@@

Although results given for the net are excellents, one of the main purposes of this paper is the implementation in real time, so the number of parameters to be computed must be a problem, so we considered to modify the net in order to improve the processing time. To achive this, it was neccesary to reduce the number of filters of cNET from 64 to 16, this permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy, the results of the processing will be explained with more detail in the next section.

@@

For this stage, we considered an extra dataset with 200 images of maize plants in stage of V3-V7 and 203 images of weed, obtained in maize crops, the results were comparated between cNET with 64 and 16 filters in the Table \ref{table:3}.\\  
\begin{table}[h!]
\centering
\begin{tabular}{|l|c|c|p{2cm}|}  
 \hline
 \multicolumn{4}{ |c| }{GPU} \\
 \hline
   cNET & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{CPU} \\
 \hline
   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification \\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{CPU Raspberry Pi 3} \\
 \hline
   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification\\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 615 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 161 s \\ [0.75ex]
  \hline
\end{tabular}
\caption{Test}
\label{table:3}
\end{table}

Like the table shown the results were achieved by the GPU processor, it is the best option to classificate a large amount of images however this project is thought to be portable, so we consider the RaspBerry Pi for the analysis of performance. With cNET of 64 filters the results fo time of classification was 615 miliseconds, so it time isn\'t the optimum for our objective that it is the processing in a real time.\\
